KidsAIR: Main analysis

### 2020-12-12 main_analysis_final.Rmd
interaction analysis updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 9 Dec 2020"
output: pdf_document
---

@@

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try child_age, gender, home_floors_2level, home_sqft_2level, residents_smoke

# Run primary model and print results
itt_results_int <- glmer(lrti_events_di_total ~ treatment_assigned*residents_smoke + 
                     child_age + 
                     person_time_at_risk + (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(itt_results_int, paste0(file_path, "Output/itt_results_int_age.rds"))
summary(itt_results_int)

int_emmeans <- emmeans(itt_results_int, pairwise ~ treatment_assigned | residents_smoke)
summary(int_emmeans, conf.int = TRUE)
confint(int_emmeans)

table(model.frame(itt_results_int)$treatment_assigned)
nobs(itt_results_int)
```

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_pm_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                       (1 | cohort:area), data = analysis_data_winter1)
#write_rds(itt_pm_results, paste0(file_path, "Output/itt_pm_results.rds"))
# Adding the randomization variable for child_age leads to the exact same model results
# Adding a random term for home adversely impacts the model since there is only one
# distinct observation per home

@@

# Run primary model and print results
itt_pm_results_int <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned*int_var + 
                              child_age + 
                       (1 | cohort:area), data = new_model_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_pm_results_int, pairwise ~ treatment_assigned | int_var)
#summary(int_emmeans, conf.int = TRUE)
save_results <- confint(int_emmeans)
save_results <<- confint(int_emmeans$contrasts)
#save_results

plot_results <- as.data.frame(save_results$contrasts) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(lower.CL)-1)*100, digits = 2),
         conf.high = round((exp(upper.CL)-1)*100, digits = 2)) %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ITT framework, PM outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "% difference in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

summary_table <<- new_model_data %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var, treatment_assigned) %>% 
  summarize("Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "n" = n(),
            "SD PM" = sd(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Median PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))

@@

int_function(analysis_data_winter1, "home_sqft_2level")

@@

# Run primary model and print results
er_results_int <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr*chimney_clean_3level + 
                          child_age + 
                          education_3level + 
                          residents_smoke + 
                          person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 10)
#write_rds(er_results_int, paste0(file_path, "Output/er_results_int_age.rds"))
#summary(er_results_int)

int_emtrends <- emtrends(er_results_int, pairwise ~ chimney_clean_3level, var = "pm_mean_sampling_period_iqr")
summary(int_emtrends, conf.int = TRUE)

table(model.frame(itt_results_int)$treatment_assigned)
nobs(itt_results_int)
```

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 11 Dec 2020"
output: pdf_document
---

@@

# Run primary model and print results
itt_results_int <<- glmer(lrti_events_di_total ~ treatment_assigned*int_var + 
                          child_age + 
                          person_time_at_risk + (1 | home:cohort:area),
                          data = new_model_data, family = binomial, nAGQ = 20)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_results_int, revpairwise ~ treatment_assigned | int_var)
#summary(int_emmeans, conf.int = TRUE)
save_contrasts_full <<- summary(int_emmeans)
save_contrasts <<- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round(estimate, digits = 2),
         conf.low = round(asymp.LCL, digits = 2),
         conf.high = round(asymp.UCL, digits = 2)) %>% 
  dplyr::select(contrast, int_var, estimate, conf.low, conf.high)
obs <<- table(model.frame(itt_results_int)$treatment_assigned)
n_table <<- table(new_model_data$int_var, new_model_data$treatment_assigned)
#save_results

plot_results <- save_contrasts %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ITT framework, LRTI outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "Odds of LRTI vs placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

pm_summary_table <<- new_model_data %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var, treatment_assigned) %>% 
  summarize("Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "n" = n(),
            "SD PM" = sd(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Median PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))

int_function(analysis_data, "residents_smoke")
n_table
save_contrasts
pm_summary_table
save_contrasts_full

# Try child_age, gender, home_floors_2level, home_sqft_2level, residents_smoke
```

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_pm_results <- lmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                       (1 | cohort:area), data = analysis_data_winter1)
#write_rds(itt_pm_results, paste0(file_path, "Output/itt_pm_results.rds"))
# Adding the randomization variable for child_age leads to the exact same model results
# Adding a random term for home adversely impacts the model since there is only one
# distinct observation per home

@@

# Run primary model and print results
itt_pm_results_int <<- lmer(log(pm_mean_sampling_period) ~ treatment_assigned*int_var + 
                              child_age + 
                       (1 | cohort:area), data = new_model_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_pm_results_int, revpairwise ~ treatment_assigned | int_var)
#summary(int_emmeans, conf.int = TRUE)
save_contrasts_full <<- summary(int_emmeans)
save_contrasts <<- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(lower.CL)-1)*100, digits = 2),
         conf.high = round((exp(upper.CL)-1)*100, digits = 2)) %>% 
  dplyr::select(contrast, int_var, estimate, conf.low, conf.high)
obs <<- table(model.frame(itt_pm_results_int)$treatment_assigned)
n_table <<- table(new_model_data$int_var, new_model_data$treatment_assigned)
#save_results

plot_results <- save_contrasts %>% 
  ggplot(aes(group = contrast, shape = contrast)) +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ITT framework, PM outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "% difference in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

pm_summary_table <<- new_model_data %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var, treatment_assigned) %>% 
  summarize("Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "n" = n(),
            "SD PM" = sd(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Median PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))

@@

int_function(analysis_data_winter1, "burn_level_3level")
n_table
save_contrasts
pm_summary_table
save_contrasts_full

@@

# Run primary model and print results
er_results_int <- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr*child_age + 
                          #child_age + 
                          education_3level + 
                          residents_smoke + 
                          person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = analysis_data_winter1, family = binomial, nAGQ = 20)
#write_rds(er_results_int, paste0(file_path, "Output/er_results_int_age.rds"))
#summary(er_results_int)

int_emtrends <- emtrends(er_results_int, pairwise ~ child_age, var = "pm_mean_sampling_period_iqr")
summary(int_emtrends, conf.int = TRUE)

nobs(itt_results_int)
```

# Run primary model and print results
er_results_int <<- glmer(lrti_events_di_winter ~ pm_mean_sampling_period_iqr*int_var + 
                          #child_age + 
                          education_3level + 
                          residents_smoke + 
                          person_time_at_risk_winter +
                          (1 | home:cohort:area), 
                          data = new_model_data, family = binomial, nAGQ = 20)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emtrends <- emtrends(er_results_int, pairwise ~ int_var, var = "pm_mean_sampling_period_iqr")

save_contrasts <<- confint(int_emtrends$emtrends) %>% 
  mutate(estimate = round(pm_mean_sampling_period_iqr.trend, digits = 2),
         conf.low = round(asymp.LCL, digits = 2),
         conf.high = round(asymp.UCL, digits = 2)) %>% 
  dplyr::select(int_var, estimate, conf.low, conf.high)

plot_results <- save_contrasts %>% 
  ggplot() +
  geom_point(aes(x=int_var, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=int_var, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Interaction contrasts for ER framework, LRTI outcome",
          subtitle = paste0("Interaction term = ", interaction_var)) +
  labs(y = "Odds of LRTI IQR increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black"))

pm_summary_table <<- new_model_data %>% 
  filter(!is.na(int_var)) %>% 
  group_by(int_var) %>% 
  summarize("Mean PM" = mean(pm_mean_sampling_period, na.rm = TRUE),
            "n" = n(),
            "SD PM" = sd(pm_mean_sampling_period, na.rm = TRUE),
            "Min PM" = min(pm_mean_sampling_period, na.rm = TRUE),
            "Median PM" = median(pm_mean_sampling_period, na.rm = TRUE),
            "Max PM" = max(pm_mean_sampling_period, na.rm = TRUE))

int_function(analysis_data_winter1, "child_age")
save_contrasts
pm_summary_table

# Try child_age, gender, home_floors_2level, home_sqft_2level, residents_smoke
```
